\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}

% Reduce space before/after sections
\titlespacing{\section}{0pt}{6pt}{4pt}

\begin{document}

\begin{center}
    \textbf{\Large Kevin Waran} \\
    Ajax, ON - \href{mailto:warankevin7@gmail.com}{warankevin7@gmail.com} -  (647)-562-9777 -\href{https://www.linkedin.com/in/kevin-waran-16aa75267}{LinkedIn}  - \href{https://github.com/kevin-waran} {Github}
\end{center}

\vspace{0.5em}

\section*{EDUCATION}
\textbf{Ontario Tech University} \hfill September 2021 - Current \\
Bachelor of Computer Science

\section*{EXPERIENCE}

\textbf{TOWN OF AJAX} \hfill August 2024 - Current \\
\textit{Customer Service Representative}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Delivered exceptional customer service by resolving client concerns, responding promptly to high volumes of phone calls and emails, and ensuring accurate dissemination of Town programs, memberships, and event information.
    \item Processed registrations and cash transactions with precision, maintained confidentiality of client data, and collaborated with program coordinators to provide tailored solutions, enhancing the overall client experience.
\end{itemize}

\textbf{CITY OF TORONTO} \hfill September 2021 - Current \\
\textit{Facility In-Charge}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Provided excellent customer service and resolved issues promptly, ensuring safe and engaging recreational program delivery.
    \item Supervised staff, coordinated facility setups, and managed incidents with strong problem-solving skills to maintain smooth operations.
\end{itemize}

\textbf{PLAYFOREVER} \hfill March 2024 - August 2024 \\
\textit{Web Developer}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Revamped Playforever’s website to create a more user-friendly experience, resulting in a 35\% increase in web traffic and a 20\% increase in program sign-ups within 3 months of launch.
    \item Implemented responsive design and optimized the website’s navigation, boosting user engagement by 40\% and lowering bounce rates by 25\% for key program pages.
\end{itemize}

\textbf{CANADIAN MUSIC COOPERATIVE}

\textit{IT Team} \hfill September 2023 - December 2023
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Resolved 50+ IT support tickets across various departments, ensuring seamless operations and minimizing technical disruptions.
    \item Collaborated with HR to streamline the onboarding process for 10+ new hires, reducing onboarding time by 25\% through efficient system setup and support.
\end{itemize}

\textit{Data Specialist} \hfill July 2023 - September 2023
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Enhanced data accuracy by restructuring Google Sheets to efficiently track event attendance, contributing to a 25\% increase in reporting precision for weekly music events.
    \item Streamlined team workflows by addressing and resolving Google tickets, demonstrating strong problem-solving, teamwork, and communication skills to maintain smooth project operations.
\end{itemize}

\section*{PROJECTS}

\textbf{MoodTracker}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Developed and deployed a full-stack journaling application using React for the frontend and Flask for the backend, enabling secure mood tracking and journaling features.
    \item Integrated RESTful APIs for seamless communication between the client and server, ensuring efficient data handling and incorporating weather-based mood insights.
\end{itemize}

\textbf{ChatServer}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Developed a scalable chat server using Java and RESTful API principles, ensuring real-time communication and secure user authentication across platforms.
    \item Engineered a modular API architecture in Java, enabling seamless integration and future expansion for cross-platform communication systems.
\end{itemize}

\section*{TECHNICAL SKILLS}

\textbf{Technical Support Tools:} Knowledgeable in SQL Server, SSRS, MS Office. \\
\textbf{Languages \& Frameworks:} Python, Java, SQL, HTML5, CSS, JavaScript, C++, C\# \\
\textbf{Databases \& Tools:} MySQL, MongoDB, PostgreSQL, Firebase, Git, Postman.

\end{document}
